\section{Literature Review}
Literature Review

A literature review demonstrates to your reader that you are able to:

Understand and critically analyse the background research
Select and source the information that is necessary to develop a context for your research
It also:

Shows how your investigation relates to previous research
Reveals the contribution that your investigation makes to this field (fills a gap, or builds on existing research, for instance)
Provides evidence that may help explain your findings later

What research has already been done on this topic?
What are the sub-areas of the topic you need to explore?
What other research (perhaps not directly on the topic) might be relevant to your investigation?
How do these sub-topics and other research overlap with your investigation?

part 1 broad overview

This paper is the result of (a) previous paper(s) by

Developing network protocols are becoming more and more complex to meet high demands. These demands often related to reliability, security and efficiency. As a result of these demands, the implementation of such a protocol can be a demanding and challenging task to perform. A protocol that cantains many rules and definitions and the code must implement these rules to their fullest

Protocols way have many  as the protocol often defines extremely specific


Implementing a protocol that meet these e
today to meet todays news demands (source)
Protocols often use terms such as required, must, must not, should and should not, 


Developing and implementing network protocols is a complex task. Protocols have highly specified rules of how it should react to various types of events. Some of this complexity can not be avoided, it is an essential complexity. However, it is possible to reduce the complexity regarding the tools used to implement the protocol, the accidental complexity.

This paper is the result of (a) position paper written by Saleem Bhatti, Edwin Brady, Kevin Hammond and James McKinna. It discusses the complexity of implementing advanced network protocols. The paper 


http://en.wikipedia.org/wiki/Programming_complexity
